An inquiry into the influence of parallelism and the choice of random engines on the runtime and results of Stride

### 2018-03-10 assets/src/week4/paper/main.tex
Update plots for paper week 4

\begin{table}[!hbt]
    \begin{tabular}{c c c c c c}
       \textbf{lgc64} & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} & \textbf{yarn3}\\
        0.8231 & 0.4216 & 0.9115 & 0.4199 & 0.1473 & 0.0.4431
    \end{tabular}
    \caption{P-values of the Measles 16 test case for the Shapiro-Wilkes normality test}
    \label{tab:measles_16:shapiro}
\end{table}

@@

@@

\begin{figure}%
   	\makebox[\textwidth][c]{%
   		\centering%
   		\subfloat[Boxplot of Influenza A run with \texttt{lgc64}]{%
   			{\includegraphics[width=0.5\textwidth]{images/boxplot_lgc64.png}}%
   		}%
   		\qquad%
   		\subfloat[Boxplot of Influenza A run with \texttt{lgc64\_shift}]{%
  			{\includegraphics[width=0.5\textwidth]{images/boxplot_lgc64_shift.png}}%
   		}%
   	}\\
   	\makebox[\textwidth][c]{%
   		\centering%
   		\subfloat[Boxplot of Influenza A run with \texttt{mrg2}]{%
   			{\includegraphics[width=0.5\textwidth]{images/boxplot_mrg2.png}}%
   		}%
   		\qquad%
   		\subfloat[Boxplot of Influenza A run with \texttt{mrg3}]{%
  			{\includegraphics[width=0.5\textwidth]{images/boxplot_mrg3.png}}%
   		}%
   	}\\
   	\makebox[\textwidth][c]{%
   		\centering%
   		\subfloat[Boxplot of Influenza A run with \texttt{yarn2}]{%
   			{\includegraphics[width=0.5\textwidth]{images/boxplot_yarn2.png}}%
   		}%
   		\qquad%
   		\subfloat[Boxplot of Influenza A run with \texttt{yarn3}]{%
  			{\includegraphics[width=0.5\textwidth]{images/boxplot_yarn3.png}}%
   		}%
   	}%
   	\caption{Running time in function of number of threads}

\end{figure}

>>>>

\begin{table}[!hbt]
    \begin{tabular}{c c c c c c}
       \textbf{lgc64} & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} & \textbf{yarn3}\\
        0.8231 & 0.4216 & 0.9115 & 0.4199 & 0.1473 & 0.4431
    \end{tabular}
    \caption{P-values of the Measles 16 test case for the Shapiro-Wilkes normality test}
    \label{tab:measles_16:shapiro}
\end{table}

@@

A few of the plots can be seen in \cref{fig:normality}, and for those who would like to see more of them, they can be generated with the script and datafiles found at \url{TODO TODO TODO}. % TODO: update url once published to gh-pages

\begin{figure}%
   	\makebox[\textwidth][c]{%
   		\centering%
   		\subfloat[QQ plot of Influenza A results with \texttt{lgc64}]{%
   			{\includegraphics[width=0.5\textwidth]{images/influenza_qq_lgc64.png}}%
   		}%
   		\qquad%
   		\subfloat[Histogram of Influenza A results with \texttt{lgc64}]{%
  			{\includegraphics[width=0.5\textwidth]{images/influenza_histo_lgc64.png}}%
   		}%
   	}\\
   	\makebox[\textwidth][c]{%
   		\centering%
   		\subfloat[QQ plot of Measles 16 results with \texttt{mrg2}]{%
   			{\includegraphics[width=0.5\textwidth]{images/measles_qq_mrg2.png}}%
   		}%
   		\qquad%
   		\subfloat[Histogram of Measles 16 results with \texttt{mrg2}]{%
  			{\includegraphics[width=0.5\textwidth]{images/measles_histo_mrg2.png}}%
   		}%
   	}%
   	\label{fig:normality}
   	\caption{Visually evaluating the normality of the attack rate}
\end{figure}

@@
